ohun: an R package for optimizing automatic acoustic signal detection

### 2022-07-13 manuscript/manuscript.Rmd
manually change docx

---
title: 'ohun: an R package for optimizing automatic acoustic signal detection'
author:
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: no
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
always_allow_html: yes
bibliography: combined_bibs.bib
citation-style: apa.csl
link-citations: yes
editor_options:
  chunk_output_type: console
---

@@

Animal acoustic signals are widely used to investigate a variety of questions in highly diverse areas, ranging from neurobiology to community ecology and evolutionary biology. The wide usage of animal sounds in research is partly due to the fact that they can be easily registered using non-intrusive methods, can be obtained in a variety of settings from laboratories to natural areas, and the equipment required for registering an analyzing these signals has become increasingly inexpensive. In addition, the existence of online repositories and growing number has facilitated the study of these traits at larger taxonomic and geographic scales. However, the adoption of bioacustic approaches in research can also imply large amounts of data (i.e. lots of recordings), which can be challenge to analyzed manually by human observers. As a result, a growing number of computational tools for the analysis of acoustic features on those signals is increasingly available (reviewd by @Stowell2022), reflecting the need of automated approaches for efficiently conducting these analyses.

>>>>

---
title: 'ohun: an R package for optimizing automatic acoustic signal detection'
author:
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '3'
always_allow_html: yes
bibliography: combined_bibs.bib
citation-style: apa.csl
link-citations: yes
editor_options:
  chunk_output_type: console
---

@@

Animal acoustic signals are widely used to investigate a variety of questions in highly diverse areas, ranging from neurobiology to community ecology and evolutionary biology. The wide usage of animal sounds in research is partly due to the fact that they can be easily registered using non-intrusive methods, can be obtained in a variety of settings from laboratories to natural areas, and the equipment required for registering an analyzing these signals has become increasingly inexpensive. In addition, the existence of online repositories and growing number has facilitated the study of these traits at larger taxonomic and geographic scales. However, the adoption of bioacustic approaches in research can also imply large amounts of data (i.e. lots of recordings), which can be challenge to analyzed manually by human observers. As a result, a growing number of computational tools for the analysis of acoustic features on those signals is increasingly available (reviewed by @Stowell2022), reflecting the need of automated approaches for efficiently conducting these analyses.
